### 2020-02-29 ChapterIntroduction/chapterIntroduction.tex
Updated: Outline reflects changes in Background

\section{Outline}
%TODO: Make sure this is up to date
The following section provides an outline for this study:
2. Background and Related Work:
\begin{itemize}
	%Context
	\item Real-time physics engines overview. The reader is introduced to the topic of physics simulations and real-time and non-real-time physics simulations are compared. The following are defined: terms; workings; important and relevant aspects, e.g. body types; uses in games and simulations; typical scales and performance of real-time simulations; and performance budget in real-time applications.
	\item Scalable Non-Real Time Physics. Previous work and applications of scalable non-real time physics and how those techniques are not suitable for use in real-time physics simulations are discussed.
	\item Online gaming. The wider topic of online gaming (client-hosted, P2P, server) is discussed, including the challenges of latency, security/cheating and computational limits. Also some details of online gaming servers are discussed, specifically, typical server frame-times and network tick updates. 
	\item Physics in online gaming (and the lack of, due to the challenges faced).
	%Relevant Related Work
	\item Graph-partitioning. When it comes to spatially-partitioning a simulation, the problem is essentially a graph partitioning problem, where objects are nodes and if there is a possible interaction, an edge exists. Useful for terms, comparisons with and future work on load-balancing will heavily involve this.
	\item Distributed virtual environments. Existing ways of distributing game worlds are reviewed and previous work carried out on these approaches. These fall into two categories, migratory (approach used by AP) and non-migratory. The studies found non-migratory to be the better solution when focusing on player-player interaction and why migratory is the better solution for physics body-physics body interaction will be discussed. Important concepts such as interest management are introduced to the reader.
	\item Distributed Real-time Physics. Previous work looking specifically at distributing real-time physics will be reviewed and how AP differs from these approaches.
	\item Cloud Computing. The wider context of cloud computing will be discussed and how AP is deployed on the cloud and also specifically conditions that affect AP in the cloud, i.e. latency and packet-loss
	%Applications
	\item Scientific and Engineering simulations. Real-time simulations are being used more in scientific research, however these are limited to what can be achieved on a single machine. AP allows real-time physics simulations to be scaled, enabling large or complex simulations that otherwise wouldn't have been able, to run in real-time.
	\item Containerisation of Game Engines. Game engines, generally, currently run as one single application, including graphics, physics, AI etc. (with the exception of databases for user data). AP separates out the physics element into its own container, much like many modern systems are splitting up different aspects of systems into their own containers, for example web applications. This containerisation of physics, means, physics can be elastically scaled independently from other systems such as graphics, along with other advantages of modularity.
	\item Streamed Gaming. The main foreseeable application of AP is Streamed Gaming, with the use of large multiplayer worlds, that are persistent and scalable with dedicated and elastic physics nodes. Physics is no longer limited to what can be simulated on a single machine and co-located render nodes solves the issue of higher latencies between the render node and physics simulation, the main problem with the use of physics in online gaming.
\end{itemize}

>>>>

\section{Outline}
%TODO: Make sure this is up to date
The following section provides an outline for this study:
2. Background and Related Work:
\begin{itemize}
	%Context
	\item Real-time physics engines overview. The reader is introduced to the topic of physics simulations and real-time and non-real-time physics simulations are compared. The following are defined: terms; workings; important and relevant aspects, e.g. body types; uses in games and simulations; typical scales and performance of real-time simulations; and performance budget in real-time applications.
	\item Scalable Non-Real Time Physics. Previous work and applications of scalable non-real time physics and how those techniques are not suitable for use in real-time physics simulations are discussed.
	\item Online gaming. The wider topic of online gaming is discussed, including the main challenges faced and typical architectures used (client-sever, peer-to-peer, distributed servers). Important aspects to this study's work are also discussed, specifically, typical server frame-times and network tick updates, delta-encoding and protocols. 
	\item RakNet. A brief overview is given of the important features of RakNet, the network library used in this study's implementation (AP).
	\item Consistency in Real-Time Physics. The challenges of consistency in physics are addressed. The client-side compensation technique of dead-reckoning is discussed and how it creates consistency problems.
	%Relevant Related Work
%	\item Graph-partitioning. When it comes to spatially-partitioning a simulation, the problem is essentially a graph partitioning problem, where objects are nodes and if there is a possible interaction, an edge exists. Useful for terms, comparisons with and future work on load-balancing will heavily involve this.
	\item Distributed virtual environments. Existing ways of distributing game worlds are reviewed and previous work carried out on these approaches. These fall into two categories, migratory (approach used by AP) and non-migratory. The studies found non-migratory to be the better solution when focusing on player-player interaction and why migratory is the better solution for physics body-physics body interaction will be discussed. Important concepts such as interest management are introduced to the reader.
	\item Distributed Real-time Physics. Previous work looking specifically at distributing real-time physics will be reviewed and how AP differs from these approaches.
	\item Cloud Computing. The wider context of cloud computing will be discussed and how AP is deployed on the cloud and also specifically conditions that affect AP in the cloud, i.e. latency and packet-loss
	%Applications
	\item Real-time Physics for Scalable Simulations. Real-time simulations are being used more in scientific research, however these are limited to what can be achieved on a single machine. AP allows real-time physics simulations to be scaled, enabling large or complex simulations that otherwise wouldn't have been able, to run in real-time.
	\item Microservices for Game Engines. Game engines, generally, currently run as one single application (monolith), including graphics, physics, AI etc. (with the exception of databases for user data). AP separates out the physics element into its own microservice, much like many modern systems are splitting up different aspects of systems into their own microservices, for example web applications. This separation of physics into a microservice means physics can be elastically scaled independently from other systems such as graphics, along with other advantages of modularity.
	\item Streamed Gaming. The main foreseeable application of AP is Streamed Gaming, with the use of large multiplayer worlds, that are persistent and scalable with dedicated and elastic physics nodes. Physics is no longer limited to what can be simulated on a single machine and co-located render nodes solves the issue of higher latencies between the render node and physics simulation, the main problem with the use of physics in online gaming.
\end{itemize}
